### 2013-09-16 chi2014/goals.tex
some results discussion

\textbf{Hypothesis 2:} there is a set general, common ideas that make up the first several responses of every crowd brainstorming session, regardless of condition.

@@

\begin{itemize}
\item \textbf{Hypothesis 3:} An idea from one semantic category should more often be followed by an idea from the same category than expected by random chance
\item \textbf{Hypothesis 4:} idea generation when changing semantic categories takes longer than when repetiting categories
\end{itemize}

Parnes et al \cite{parnes_effects_1961} showed that more high quality ideas were generated in the latter half of brainstorming run than the former half. In keeping of our philosophy regarding creativity and quality measurements, we restrict the content of this test to originality. \textbf{Hypothesis 5:} Ideas generated in the latter half of a brainstorming session are of higher originality than ideas generated in the former half.

>>>>

In addition, we expect this saturation to occur at a different rate between the conditions. \textbf{Hypothesis 2:} the rate of new ideas will reduce to 0 in some conditions more quickly than others.

\textbf{Hypothesis 3:} there is a set general, common ideas that make up the first several responses of every crowd brainstorming session, regardless of condition.

@@

\begin{itemize}
\item \textbf{Hypothesis 4:} An idea from one semantic category should more often be followed by an idea from the same category than expected by random chance
\item \textbf{Hypothesis 5:} idea generation when changing semantic categories takes longer than when repetiting categories
\end{itemize}

Parnes et al \cite{parnes_effects_1961} showed that more high quality ideas were generated in the latter half of brainstorming run than the former half. In keeping of our philosophy regarding creativity and quality measurements, we restrict the content of this test to originality. \textbf{Hypothesis 6:} Ideas generated in the latter half of a brainstorming session are of higher originality than ideas generated in the former half.

### 2013-09-16 chi2014/method.tex
some results discussion

In order to develop an adequate model of baseline brainstorming performance in crowd marketplaces, it was necessary to establish a corpus of data. Over the course of four months we repeatedly collected responses to brainstorming tasks. Throughout the experimental process, particular aspects of the experimental design remained fixed.

The independent variables of interest were \emph{brainstorming problem} and \emph{number of ideas requested}.

Participants were recruited from Amazon's \emph{Mechanical Turk} (CITE), and were restricted to residents of the United States for a baseline expectation of english language comprehension and cultural familiarity. Mechanical Turk is an online marketplace in which members receive financial reward for completing \emph{Human Intelligence Tasks}, or HITs.

HITs were placed on the marketplace for each \emph{number of ideas requested} condition, with proportional rewards. Participants could accept at most one HIT in each of these conditions.

Upon accepting a HIT, participants were randomly assigned into a \emph{brainstorming problem} condition. We ensured that participants completing multiple HITs are not exposed to the same brainstorming task twice.

\subsubsection{Design Concerns}
Workers choose which HITs to complete, thus self-selection bias is a reasonable concern. This bias is also present in real-world HIT choice behaviour.

Upon accepting a HIT, participants were asked to give consent and informed that they could leave the study at any point without financial consequences. In regular online task markplaces, common practice would restrict workers from submitting a HIT as complete unless all responses were given. This is a threat to external validity.

@@

The brainstorming task is below this, followed by a series of text entry inputs numbered through to the total number of ideas requested. Figure X (FIG) is an example of a typical task. We place a larger free text area at the bottom of the list where participants could enter any additional ideas.

\subsection{Pilots and Question Selection}

With this basic design in hand, we ran several pilots and experiments. In early pilots, we used classic problems from psychology literature on brainstorming, including the "thumb problem" and "broom problem" (CITE). Early results from brainstormers were unsatisfying and wildly divergent. We identified three key traits problems needed in order to evaluate them for creativity:

\begin{enumerate}
\item They must require creativity to resolve. Obvious answers do not satisfy the problem.
\item They must be problems that participants on Mechanical Turk would have the expertise to solve.
\item They must have an associated success metric.
\end{enumerate}

The primary researcher and two additional researchers familiar with crowd marketplace brainstorming tasks brainstormed a large variety of potential problems. These problems were iterativelly culled and refined over a series of further pilots until the above goals were felt to be achieved. This resulted in the following four questions, as presented to the participants:

\begin{enumerate}
\item \textbf{Charity}

The Electronic Frontier Foundation (EFF) is a nonprofit whose goal is to protect individual rights with respect to digital and online technologies. For example, the EFF has initiated a lawsuit against the US government to limit the degree to which the US surveils its citizens via secret NSA programs. If you are unfamiliar with the EFF and its goals, read about it on its website (https://www.eff.org) or via other online sources (such as Wikipedia).

Brainstorm N \emph{new} ways the EFF can raise funds and simultaneously increase awareness. Your ideas \emph{must be different from their current methods}, which include donation pages, merchandise, web badges and banners, affiliate programs with Amazon and eBay, and donating things such as airmiles, cars, or stocks. See the full list of their current methods here: https://www.eff.org/helpout. Be as specific as possible in your responses."

\item \textbf{Mechanical Turk}

"Mechanical Turk currently lacks a dedicated mobile app for performing HITs on smartphones (iPhone, Androids, etc.) or tablets (e.g., the iPad).

Brainstorm N features for a mobile app to Mechanical Turk that would improve the worker's experience when performing HITs on mobile devices. Be as specific as possible in your responses.

\item \textbf{MP3}

Many people have old MP3 players or MP3 players that they no longer use. Please brainstorm N uses for old MP3 players/MP3 players. Assume that the devices' batteries no longer work, though they can be powered via external power sources. Also be aware that devices may \emph{not} have displays. Be as specific as possible in your descriptions.

\item \textbf{Forgot Name}

Imagine you are in a social setting and you have forgotten the name of somebody you know. Brainstorm N ways you could learn their name without directly asking them. Be as specific as possible in your descriptions.

\end{enumerate}

Classic brainstorming procedure asks for as many ideas as possible in a period of time. We instead asked participants for a specific number of responses: 5, 10, 20, 50, 75 or 100.

This decision was motivated by our early experience asking respondants to simply come up with "as many ideas as possible" in a generous time frame. Over N respondents, we received a mean of N ideas (std N), despite giving a financial reward N times that of any of our explicitly numbered conditions. This unlimited condition provided a great deal of leeway for participants to "game the system", and receive the full reward with very little work, so we dropped the condition.

\subsection{Experiment}

With the above problem set and the previously outlined task design (SEC), we collected responses. We chose 6 \emph{number of ideas requested} conditions that covered the spectrum (and beyond) of quantity of creativity requested from a single participant. Those conditions were: 5 ideas (with a corresponding reward of \$0.18 USD), 10 ideas (\$0.35), 20 (\$0.70), 50 (\$1.75), 75 (\$2.65), and 100 (\$3.50). To reiterate, participants chose a HIT to generate some number of ideas, and then were randomly assigned a problem.

@@

In total, 341 HITs were complteed by 280 distinct participants. A breakdown of responses across conditions is given in table TAB. In cases when a single participant answered the same question multiple times, all HITs after the first were dropped for subsequent analysis.

\begin{tabular}[h!]{r | l l l l l l }
& 5 & 10 & 20 & 50 & 75 & 100 \\ \hline \hline
HITs (MP3) & 59 & 49 & 23 & 10 & 10 & 10 \\
HITs unique (MP3) & 57 & 39 & 21 & 9 & 10 & 10 \\ \hline
HITs (Turk) & 11 & 10 & 11 & 10 & 9 & 9 \\
HITs unique (Turk) & 11 & 9 & 11 & 9 & 9 & 7 \\ \hline
HITs (Forgot) & 10 & 10 & 10 & 12 & 11 & 11 \\
HITs unique (Forgot) & 10 & 8 & 9 & 12 & 10 & 10 \\ \hline
HITs (Charity) & 9 & 10 & 10 & 8 & 10 & 9 \\
HITs unique (Charity) & 9 & 9 & 10 & 7 & 9 & 9 \\ \hline
HITs (total) \\
HITs unique (total) \\ \hline
\end{tabular}

There is significantly more data for the MP3 condition than for any of the others. Despite at least 7 unique HITs for each of the 24 problem x number conditions, we found that the limited number of total responses for the 5, 10 and 20 conditions precluded significant analysis. To that end, we selected the MP3 player problem to further expand the data set to 400 (TODO: maybe not true) responses per number condition.

HITs were augmented with JavaScript to collect data in addition to brainstorming responses. For each response, we collected the time of the first activation and last de-activation of the form element. We collected the time the HIT was accepted and the time it was submitted. We took a has of the Mechanical Turk worker ID as a unique identifier of our participants.

@@

As we began to examine the data, it quickly began apparent that there are nuances in discussing responses to brainstorming tasks. In the interest of facilitating this discussion, we introduce terms here that will be used for the remainder of the paper.

An \emph{instance} is a single response by a single participant to a brainstorming question. For example, Figure FIG gives four \emph{instances} provided in the \emph{MP3 player} brainstorming task.

\begin{figure}[!h]
    \begin{enumerate}
        \item "Use as a mirror"
        \item "Mirror"
        \item "Use it as a mirror for makeup"
        \item "Tape it to a telephone pole and use as a reflector"
    \end{enumerate}
\end{figure}

An instance is associated with exactly one \emph{idea}. An idea may have 0 or more instances, all of which describe an identical solution to a problem. In Figure FIG, "Use as a mirror" and "Mirror" belong to the same \emph{idea}. However, "Use it as a mirror for makeup" does not belong to the same idea, as it adds additional information to the problem solution; it is more specific.

Despite this, it is clear the ideas have some commonality. It is desireable to encode this relationship. To that end, we organize ideas in \emph{category trees}. In a category tree, ideas act as nodes. Each idea may have 0 or 1 parent idea (only the root has 0) and 0 or more child ideas. An example category tree for the instances in Figure FIG is given in Figure FIG.

@@

If an idea \emph{A} is a parent of idea \emph{B}, A is a generalization of B: all instances in A are are suitably general to encompass all instances in B. This difference is relative to the ideas in question.

A \emph{question forest} is simply the collection of all category trees generated in response to a particular question. Different trees in a question forest have no special relationship in meaning.

\subsection{Coding}

One researcher coded responses the MP3 problem to produce an idea forest as described above. The MP3 problem was chosen because it was subjectively easiest to distinguish between and categorize ideas.

The clustering algorithm is described in Figure FIG. Instances are added one at a time to the existing idea forest. In brief summary, the root idea that most closely matches the strategy in the instance is selected, and then that root idea and the new instance are compared in generality. This process may be repeated depending on this generality relationship, until instance is either placed in an existing idea or a new idea node is created.

@@

\subsubsection{Similarity}
Two ndodes a and b have high similarity if they solve the problem in the same way, and low similarity if their solutions have no common themes. For example, in Figure FIG, "Mirror" and "Tape it to a telephone pole and use as a reflector" have high similarity, as they both solve the problem of using a broken MP3 player by using it to reflect light.

@@

After completion of the coding algorithm, we were left with an idea forest as described in section SEC.

>>>>

In order to develop models and test hypotheses, it was necessary to establish a significant corpus of brainstorming data data. Over the course of four months we repeatedly collected responses to brainstorming tasks.

Participants were recruited from Amazon's \emph{Mechanical Turk} \cite{_amazon_????}, and were restricted to residents of the United States for a baseline expectation of english language comprehension and cultural familiarity. Mechanical Turk is an online marketplace in which members receive financial reward for completing \emph{Human Intelligence Tasks}, or HITs.

HITs were placed on the marketplace asking for a variable \emph{number of ideas}, with proportional rewards. These conditions were : 5 ideas (with a corresponding reward of \$0.18 USD), 10 ideas (\$0.35), 20 (\$0.70), 50 (\$1.75), 75 (\$2.65), and 100 (\$3.50).

This served as the independent variable in all data gathering. It must be stated that under normal brainstorming conditions, participants are asked to generate as many ideas as possible within a fixed time frame, instead of a fixed number. We excluded such a condition for two reasons. First, it is practice in crowd creativity tasks to solicit a fixed number of ideas (e.g. Yu and Nickerson \cite{yu_cooks_2011}). Secondly, we piloted asking respondants for "as many ideas as possible" in a generous time frame. Over N respondents, we received a mean of N ideas (std N), despite giving a financial of \$\$\$\$. This suggested a propensity to "game the system", a behaviour we wanted to exclude.

While the brainstorming question was manipulated in pilot studies, it was fixed for the data reported on in this paper:

\begin{itemize}
\item \textbf{MP3}

Many people have old MP3 players or MP3 players that they no longer use. Please brainstorm N uses for old MP3 players/MP3 players. Assume that the devices' batteries no longer work, though they can be powered via external power sources. Also be aware that devices may \emph{not} have displays. Be as specific as possible in your descriptions.
\end{itemize}

This problem was selected for three qualities:

\begin{enumerate}
\item It requires creativity to resolve. Obvious answers do not satisfy the problem.
\item Mechanical Turk participants have the expertise to solve the problem.
\item It has an associated success metric.
\end{enumerate}

Workers choose which \emph{number of ideas} condition to participate in, thus self-selection bias is a reasonable concern. However, this bias is also present in real-world HIT choice behaviour.

Upon accepting a HIT, participants were asked to give consent and informed that they could leave the study at any point without financial consequences. Under normal conditions, the participants would be expected to complete all responses to receive compensation.

Should we be dropping these runs, or at least testing they don't have an affect?

@@

The brainstorming problem is below this, followed by a series of text entry inputs numbered through to the total number of ideas requested. Figure X (FIG) is an example of a typical task. We place a larger free text area at the bottom of the list where participants could enter any additional ideas.

@@

In total, 161 HITs were complteed by 146 distinct participants, for a total of 3007 responses. A breakdown of responses across conditions is given in table TAB. In cases when a single participant participated in multiple conditions, all HITs after the first were dropped for subsequent analysis.

\begin{tabular}[h!]{r | l l l l l l }
& 5 & 10 & 20 & 50 & 75 & 100 \\ \hline \hline
HITs completed & 59 & 49 & 23 & 10 & 10 & 10 \\
HITs completed (no repeats) & 57 & 39 & 21 & 9 & 10 & 10 \\
solutions (no repeats) & 283 & 372 & 413 & 450 & 635 & 855 \\
\end{tabular}

HITs were augmented with JavaScript to collect data in addition to brainstorming responses. For each response, we collected the time of the first activation and last de-activation of the corresponding form element. We collected the time the HIT was accepted and the time it was submitted. To uniquely identify participants, we computed a hash of their Mechanical Turk worker ID. A hash was used to protect privacy after data release.

@@

To facilitate discussion, we introduce terms here that we will use throughout the rest of the paper.

An \emph{instance} is a single solution by a single participant to a brainstorming question. Alternatively, an instance may be thought of as the text entered into a single field in the task form. For example, figure~\ref{fig:sample_instances} gives four \emph{instances} from the data set.

\begin{figure}[!h]
    \begin{enumerate}
        \item "Use as a mirror"
        \item "Mirror"
        \item "Use it as a mirror for makeup"
        \item "Tape it to a telephone pole and use as a reflector"
    \end{enumerate}
    \label{sample_instances}
\end{figure}

A \emph{brainstorming run}, or \emph{run}, is the temporally-ordered series of instances that were received in a single HIT by a single user. As stated above, after dropping repeat data, all brainstorming runs were completed by distinct participants.

An \emph{idea} is a unique solution to the brainstorming problem. An instance is associated with exactly one \emph{idea}, and all instances in the same idea should be paraphrases of one another. In Figure FIG, "Use as a mirror" and "Mirror" belong to the same \emph{idea}. However, "Use it as a mirror for makeup" does not belong to the same idea, as it contains additional information.

Despite this, it is clear the ideas have some commonality. It is desireable to encode this relationship. To that end, we propose a hierarchical clustering of ideas in \emph{category trees}. In a category tree, ideas act as nodes. Each idea may have 0 or 1 parent idea (only the root has 0) and 0 or more child ideas. An example category tree for the instances in Figure FIG is given in Figure FIG.

@@

If an idea \emph{A} is a parent of idea \emph{B}, A is a generalization of B: all instances in A are are suitably general to encompass all instances in B. This hierarchical clustering allows us to classify ideas as simultaneously different in solution stragy but different in solution details.

We further distinguish category trees into \emph{singleton} and \emph{non-singleton} category trees. A singleton category tree is composed of only one idea node, the root. A non-singleton category tree has at least two idea nodes. We introduce non-singleton category trees as correspondents to the images in Nisjstad and Stroebe's SIAM model \cite{nijstad_how_2006}. On SIAM, the idea generation process is represented by a series of images activations within which idea production occurs. Non-singleton trees by definition represent strategies that have been produced in at least two distinct ways.

The \emph{idea forest} is the collection of all category trees. Different trees in the forest have no particular relationship.

\subsection{Clustering}

In addition to the notion of an idea forest, we also propose a clustering algorithm driven by human intelligence to create the data structure. The algorithm is described in Figure~\ref{fig:cluseringalg}. Instances are added one at a time to the existing idea forest. In brief summary, the root idea that most closely matches the strategy in the instance is selected, and then that root idea and the new instance are compared in generality. This process may be repeated depending on this generality relationship, until instance is either placed in an existing idea or a new idea node is created.

@@

\subsubsection{Similarity}
Two nodes a and b have high similarity if they solve the problem in the same way, and low similarity if their solutions have no common themes. For example, in Figure FIG, "Mirror" and "Tape it to a telephone pole and use as a reflector" have high similarity, as they both solve the problem of using a broken MP3 player by using it to reflect light.

@@

The primary author followed the algorithm to cluster the 3007 response instances into ideas and trees.

### 2013-09-16 chi2014/results.tex
some results discussion

\subsection{Between-Conditions Comparisons}

\subsubsection{Saturation of ideas}

One of our hypotheses (HYP) was that as the number of instances gathered increased, the rate of new ideas, new categories and new singleton categories would converge towards 0.

Figure FIG shows the rate of new idea, category, and non-singleton category generation  over time for each number requested conditions. These plots have been smoothed by randomly shuffling the order in which ideas were receieved 500 times and taking the mean cumulative count at each point in time, and plotting with a window size of 10. In an ideal scenario where each instance provided a new unique idea and category, the lines would horizontal across the top of the figure.

\begin{figure}
    \centering
    \includegraphics[width=0.9\columnwidth]{rate_new_idea_over_time}
    \includegraphics[width=0.9\columnwidth]{rate_new_category_over_time}
    \includegraphics[width=0.9\columnwidth]{rate_new_ns_category_over_time}
    \caption{Rate of idea generation}
\end{figure}

@@

@@

As discussed above, we use height in category tree as a measure of an ideas generality. Generality (and its reverse, sepcificity) are both potentially desireable outcomes of a brainstorming task.

The idea-height across number conditions is given in figure FIG.

\begin{figure}[h]
    \centering
    \includegraphics[width=0.9\columnwidth]{height_in_subtree}
    \includegraphics[width=0.9\columnwidth]{height_in_subtree_5}
    \caption{Generality of ideas}
\end{figure}

The top panel in Figure FIG suggests that ideas tend to be less general in the conditions where we request more ideas. However, the bottom panel, which shows generality only for the first 5 responses, has no such effect. This suggests that only answers later on in the larger request batches become less general, an effect that we further examine in the following section.

In this previous section, we showed that the rate of idea convergence, the originality of ideas, and the generality of ideas varied between the number requested conditions. These relationships are useful to understand when deciding what crowd brainstorming strategy to follow. What this birds eye view excludes is an understanding of \emph{how} these differences occur. To that end, we shift our attention to the context of a single brainstorming run.

>>>>

We can use the uniqueness measure to understand the rate at which new ideas arrive. As we gather more and more ideas in the course of an experiment, we expect that we will see fewer ideas that are not already in our idea pool. Figure FIG shows the cumulative count of ideas as a function of the number of instances gathered in the experiment. To smooth the plot, the order in which instances were received was shuffled 100 times, and the mean of the cumulative unique idea count was taken at each step.

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.9\columnwidth]{ideas_over_time}
    \caption{Cumulative idea count}
\end{figure}

The horizontal line in Figure FIG represent the idea case, in which each instance represents a different idea (i.e. every answer we receive is a new, unique idea). As expected, the rate at which ideas are gained appears to taper off.

Figure FIG more closely examines the rate, the primary property of interest. The panels, from top to bottom, are the rate at which new ideas, categories, and non-singleton categories are generated, respectively. Similar to Figure FIG, these are based on shuffling the order of instances 10000 times and taking the mean of the derivative at each point. In this case, the ideal (a 1:1:1 instance:idea:category ratio) is represented by the horizontal bar across the top of the chart.

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.7\columnwidth]{rate_new_idea_over_time}
    \includegraphics[width=0.7\columnwidth]{rate_new_category_over_time}
    \includegraphics[width=0.7\columnwidth]{rate_new_ns_category_over_time}
    \caption{Rate of idea generation}
\end{figure}

The number of ideas, categories and non-singleton each drop off exponentially over time. It is unsurprising that the number of new categories should drop off faster than the number of new ideas, as we expect that there are fewer categories of ideas than there are individual ideas themselves.

The third panel, which shows non-singleton categories over time, tells a distinctly different story from the others. While in the idea and category plots, the height-ordering of rates of generation between categories remains generally identical, there is a point of intersection and reversal in the non-singleton category plot at around the 30 instances point. Before this point, the lower conditions actually generate new categories at a \emph{faster} rate.

In lower conditions, brainstormers will quickly offer up big, popular, non-singleton categories. Beyond the inflection point, the category pool is saturated with these low-hanging fruit, and only brainstormers tasked with generating more ideas will find the smaller category. This is a more nuanced view of the tree node/instance quartiles in Section SEC; condition 5 brainstormers cover the spectrum of category sizes while condition 100 brainstormers pull from the smaller category trees in the forest.

\subsection{Hypothesis 1}

@@

\subsection{Originality}

@@

### 2013-09-16 chi2014/summary.tex
some results discussion

\section{Summary of Data}

The resulting forest was composed of 3007 instances, 1213 ideas, and 335 category trees. The number of instances, ideas and categories present in each of the number conditions is given in table TAG. In addition, table TAG shows the number of "non-singleton" categories, namely, those categories containing at least two instances. Intuitively, non-singleton categories represent those categories in which some exploration actually occured. These represent categories in which we can potentially identify the idea production phase of the SIAM model [].

\begin{tabular}[h!]{r | l l l l l l }
& 5 & 10 & 20 & 50 & 75 & 100 \\ \hline \hline
HITs & 57 & 47 & 23 & 10 & 10 & 10 \\
instances & 293 & 471 & 453 & 500 & 634 & 855 \\
ideas & 171 & 249 & 278 & 341 & 443 & 177 \\
category trees & 76 & 93 & 100 & 123 & 172 & 177 \\
non-singleton trees & 28 & 41 & 41 & 50 & 49 & 61 \\
\end{tabular}

Figure FIG shows the distribution of instances in non-singleton categories. The majority of the "mass" of instances are in trees with less than 70 instances.

% TODO: this figure needs better labeling for the second part
\begin{figure}[!h]
    \centering
    \includegraphics[width=0.9\columnwidth]{instances_in_subtrees}
\end{figure}

>>>>

\section{Summary of Idea Forest}

The resulting forest was composed of 3007 instances, 1213 ideas, 335 category trees, and 129 non-singleton category trees. These metrics are decomposed by number condition is given in table TAB. A bird's eye view of the complete idea forest is in Figure FIG.

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.9\columnwidth]{idea_forest}
    \caption{Idea Forest}
\end{figure}

\begin{table}
	\begin{tabular}[h!]{r | l l l l l l }
	\textbf{number condition} & 5 & 10 & 20 & 50 & 75 & 100 \\ \hline \hline
	HITs & 57 & 47 & 23 & 10 & 10 & 10 \\
	instances & 293 & 471 & 453 & 500 & 634 & 855 \\
	ideas & 171 & 249 & 278 & 341 & 443 & 177 \\
	category trees & 76 & 93 & 100 & 123 & 172 & 177 \\
	non-singleton trees & 28 & 41 & 41 & 50 & 49 & 61 \\
	\end{tabular}
\end{table}

The height of category trees follows a roughly Poisson distribution, with the maximum tree height observed at 5. Summary statistics across condition are in table TAB. The third quartile drops as the number condition increases. While the upper conditions still discover categories trees with heights as great as 5, they generate many more "short" trees. This suggests that the ideas generated in the upper conditions are less common.

\begin{table}
	\begin{tabular}[h!]{r | l l l l l l l}
	\textbf{number condition} & 5 & 10 & 20 & 50 & 75 & 100 & all \\ \hline \hline
	median & 2 & 2 & 2 & 2 & 2 & 2 & 2\\
	first quartile & 2 & 1  & 1 & 1 & 1 & 1 & 1\\
	third quartile & 2 & 3 &3 &3 &2 &2 & 2\\
	\end{tabular}
	\caption{Category tree height}
\end{table}

The number of nodes and number of instances are also roughly poisson distributed (Table TAB). In keeping with the findings for height, trees found in the upper number conditions are smaller than trees found in the lower conditions. The precipitous drop in median tree size suggests that in the largest condition, participants are finding rare ideas with only a few variants and less than 14 instances.

\begin{table}
\begin{tabular}[h!]{r | l l l l l l l}
	\textbf{number condition} & 5 & 10 & 20 & 50 & 75 & 100 & all \\ \hline \hline
	number of nodes& \\ \hline
	median &3&4&4&3&2&2&2 \\
	first quartile &2&1&1&1&1&1&1 \\
	third quartile &15&12&12&10&5&5&5 \\
	number of instances& \\ \hline
	median &14&12&12&9&4&4&4 \\
	first quartile &4&3&4&2&1&1&1 \\
	third quartile &48&31&29&21&14&13&13 \\
	\end{tabular}
	\caption{Number of ideas and instances in trees}
\end{table}

To better understand what this distribution of tree sizes means...
